\documentclass[a4paper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

\title{KI Project B}

\author{
Martijn Dekker  6013368 \\
Egor Dmitriev   6100120 \\
Cody Bloemhard  6231888 \\
}

\date{\today}

\begin{document}
\maketitle

\section{Exercise 1}
\label{sec:ex1}
\subsection{ex1-a}
The game state holds all the data that represents the game in the current time frame. bla bla bla.
\subsection{ex1-b}
The agent state holds all data that describes an agent in the current time frame. bla bla bla.
\subsection{ex1-c}
\begin{itemize}
\item A: II, Stack: Pile of dishes
\item B: III, Queue: Roller coaster waiting line
\item C: I, PriorityQueue: Emergency room waiting line
\end{itemize}

\section{Exercise 2}
\subsection{}


\section{Exercise 3}
\subsection{ex3-a}
That means that if there exist a path to the goal you are searching for, it will return that goal.

\subsection{ex3-b}
It is complete because the algorithm will keep searching till it found the path to the goal location or till there are no more 
possible paths to stroll, which haven't been visited before. This would happen when the stack is empty 
and that can only occur if it has tried every possible path.

\subsection{ex3-c}
It will not always be the least cost solution. This is because it tries out a path and continues it till it ends, which can
lead to the goal location. This first path it finds does not have to be the path with the least cost. 
And because it stops after finding a path it doesn't always find the least cost solution.

\subsection{ex3-d}



\section{Exercise 4}
\subsection{ex4-a}
It is complete because the algorithm will keep searching till it found the path to the goal location or till there are no more 
possible paths to stroll, which haven't been visited before.

\subsection{ex4-b}
Yes, because every step pacman can take is equal in cost the algorithm needs to find the path with the least steps.
And because it looks into every path of depth k before looking into paths of depth > k it will 
always find the least cost solution.

\subsection{ex4-c}


\end{document}